Scattering and Pair Processes in General Relativistic Ray Tracing for Neutrinos

### 2016-10-16 paper.tex
Repair confusing notation for affine parameterization

Each trajectory is parameterized by affine parameter, $\lambda$, increasing in
the direction of $\ell_\beta$. We choose $\lambda=\lambda_0$ at $x^\alpha_e$
and $\lambda=\lambda$ at $x^\alpha_o$, as in Fig.~\ref{fig:affine_param}.
\todo{choose a better notation}
According to Eqn.~\ref{eqn:geodesic_x} proper distance relates to the affine
parameter by $ds=p^t d\lambda$.
\todo{show explicitly}

\begin{figure}
  \includegraphics[width=\columnwidth]{affine_parameter_label}
  \caption{Affine parameterization of a trajectory.}
  \label{fig:affine_param}
\end{figure}

\subsection{The Rendering Equation}
\label{ssec:rendering_eqn}
\todo{type up derivation from notes}
We can integrate Eqn.~\ref{eqn:boltzmann_linear} directly,
\begin{equation}
  \label{eqn:rendering}
  f(\lambda) = f(\lambda_0) e^{-\tau(\lambda,\lambda_0)} +
  \int_{\lambda_0}^\lambda d\lambda'\,e^{-\tau(\lambda,\lambda')}
  \mathscr{K}^*(\lambda') \mathscr{S}^*(\lambda'),
\end{equation}
where the parameterization conventions are depicted in
Fig.~\ref{fig:affine_param}.

\subsection{Neutrinosurface Approximation}
\label{ssec:neutrinosurface}
\todo{derive $\tau=2/3$ approx \cite[Chap.~4]{shu1991-book_radiation},
  and \cite{miln1921-radiative_equil_1}}
In the simplified configuration of a plane-parallel atmosphere, the
rendering equation reduces to 
\begin{equation}
\label{eqn:neutrinosurface}
  f(\lambda) = f^{\rm eq}(\lambda_0),
\end{equation}
where $\tau(\lambda,\lambda_0)=2/3$.

>>>>

Each trajectory is parameterized by affine parameter, $\lambda$, increasing in
the direction of $\ell_\beta$. We label $\lambda=\lambda_e$ at $x^\alpha_e$,
as in Fig.~\ref{fig:affine_param}.
If we multiply Eqn.~\ref{eqn:geodesic_x} by $u_\alpha \equiv dx_\alpha/ds$,
we find $ds=\varepsilon \,d\lambda$ is the proper distance traversed by the
neutrino as measured by our fiducial obsever $u^\alpha$.

\begin{figure}
  \includegraphics[width=\columnwidth]{affine_parameter_label}
  \caption{Affine parameterization of a neutrino trajectory of momentum
    $p_\alpha$.
    The fiducial observer with velocity $u^\alpha$ sits at $x^\alpha_o$,
    the neutrino emission event is at $x^\alpha_e$. The affine parameter
    increases from the emission event: $\lambda_e<\lambda'<\lambda''$.}
  \label{fig:affine_param}
\end{figure}

\subsection{The Rendering Equation}
\label{ssec:rendering_eqn}
\todo{type up derivation from notes}
We can integrate Eqn.~\ref{eqn:boltzmann_linear} directly,
\begin{equation}
  \label{eqn:rendering}
  f(\lambda) = f(\lambda_e) e^{-\tau(\lambda,\lambda_e)} +
  \int_{\lambda_e}^\lambda d\lambda'\,e^{-\tau(\lambda,\lambda')}
  \mathscr{K}^*(\lambda') \mathscr{S}^*(\lambda'),
\end{equation}
where the parameterization conventions are depicted in
Fig.~\ref{fig:affine_param}.

\subsection{Neutrinosurface Approximation}
\label{ssec:neutrinosurface}
\todo{derive $\tau=2/3$ approx \cite[Chap.~4]{shu1991-book_radiation},
  and \cite{miln1921-radiative_equil_1}}
In the simplified configuration of a plane-parallel atmosphere, the
rendering equation reduces to 
\begin{equation}
\label{eqn:neutrinosurface}
  f(\lambda) = f^{\rm eq}(\lambda_e),
\end{equation}
where $\tau(\lambda,\lambda_e)=2/3$.
